---
title       : Work Package 3 
subtitle    : Isotope data
author      : Jason Lessels
job         : University of Aberdeen
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}

widgets     : mathjax           # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
github:
  user: johnDorian
  repo: work_package_3
hitheme: solarized_light
--- 

## Aquatic transport: Tracing the terrestrial–aquatic C flow in arctic hydrological systems

<b>Tasks I:</b>
> - <span class = 'red'>Use isotopic and geochemical tracers to identify sources of runoff</span>, their temporal dynamics and landscape controls at multiple spatial scales (precipitation collectors, grab sampling of streamwater and synoptic sampling)
 
> - <span class = 'red'>Identify differences in source / age of aquatic C (POC, DOC, CO2 and CH4) using $\delta$13C and 14C</span> in areas with and without permafrost,  linking these differences to changes in <span class = 'red'>hydrological functioning and the soil C pool</span> (passive/composite and instantaneous isotopic sampling methods for the determination of $\delta$13C and 14C)

> - To develop empirically-informed conceptual understanding of arctic hydrological systems to address hypotheses / questions in <b>WPs 1-2</b>; 

> - <span class = 'red'>To develop a tracer-based empirical understanding</span> of catchment function to <span class = 'red'>inform and constrain low-parameter hydrological models</span> in <b>WP4</b>. 

---
## Aquatic transport: Tracing the terrestrial–aquatic C flow in arctic hydrological systems (cont.)

```{r}
summary(cars$dist)
summary(cars$speed)
```

---
---
## Plot test

```{r}
plot(1)
```