---
title       : Work Packages 3 and 4
subtitle    : Isotope data
author      : Jason Lessels
job         : University of Aberdeen
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}

widgets     : mathjax           # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
github:
  user: johnDorian
  repo: work_package_3
hitheme: solarized_light
--- 

<!-- Limit image width and height -->
<style type='text/css'>
img {
    max-height: 560px;
    max-width: 964px;
}
</style>

<!-- Center image on slide -->
<script src="http://ajax.aspnetcdn.com/ajax/jQuery/jquery-1.7.min.js"></script>
<script type='text/javascript'>
$(function() {
    $("p:has(img)").addClass('centered');
});
</script>

## Using isotopic and geochemical tracers to identify sources of runoff

<b>Aims and objectives</b>

1. Identify the main sources of water at the catchment scale.
2. Use this information to improve the understanding of the sources and fate of C through the catchment.

<b>How we will use the data</b>

- <span class='red'>Precipitation samples</span>: Identify the isotopic signature of precipitation inputs
- <span class='red'>Soil water</span>: Identify isotopic signature to monitor mixing of soil water and precipitation and the travel time from soil to the stream.
- <span class='red'>Stream sampling (catchment outlet)</span>: Detect seasonal trends and allow for the calibration of estimated transit times.

---
## How to use isotopes to trace water ##
<b> plot of GMWL explanation</b>

---
## Data summary ##

Data           | Frequency | Objective
---------------|-----------|----------
Synoptic sampling | multiple times throughout 13 and 14 | Examine small scales controls
Extra synoptic sites | 2 visits (2014) |  Incorporated into a network geospatial model
Stream discharge  | (15 min - 2014) | Estimating loads and hydrological modelling
Soil water | multiple times at 2 depths (4 locations) during 2014 | Used in estimating transit times and identifying production and sources of DOC
Rainfall collection | throughout 2013 and 2014 | Used as input to transit time modelling
CDOM | (2 weeks during 2014) | Continuous estimates of DOC 


---
## Time series plot##
```{r, echo=FALSE, }
library(ggplot2)
library(gridExtra)

ls()
```

<b> Time series plot of all the data</b>

---
## Isotope overview ##
<b> plot of isotopes with colours and split into years</b>

---
## Spatial isotopes (lakes etc) ##
<b> plot of isotopes across the lakes</b>

---
## Soil water Isotopes##
<b> Soil water isotope plots with aspect diffs</b>

---
## CDOM data ##
<b> plot of CDOM data</b>

---
## Where to from here ##
Outline what wil be done from this point.
EGU etc.

---
## Work Package 4 ##
Something about intergrating everything

--- 
## Aims and objectives ##

---


## ECOSSE model Outline ##

---

## Wolf Creek overview ##

---
##  Model outline ##

---
## Observed data from Wolf Creek ##

```{r, echo = FALSE, warning=FALSE,message=FALSE, fig.width=12, fig.height=5}
load("plots_for_talk.rdata")

obs_plot

```

---

##  Stream discharge simulations ##

```{r,echo = FALSE, warning=FALSE, message=FALSE, fig.width=12, fig.height=5}
load("plots_for_talk.rdata")
q_val_plot
```

---

##  DOC simulations ##

```{r, echo = FALSE, warning=FALSE,message=FALSE, fig.width=12, fig.height=5}
load("plots_for_talk.rdata")
doc_val_plot
```

---

##  An example ##

```{r ,echo = FALSE, warning=FALSE,message=FALSE, fig.width=14, fig.height=5}
load("plots_for_talk.rdata")
year_2008_plot
```

---

##  An example ##

```{r, echo = FALSE, warning=FALSE,message=FALSE, fig.width=8, fig.height=8}
load("plots_for_talk.rdata")
sw_plot
```

---

##  An example ##

```{r, echo = FALSE, warning=FALSE,message=FALSE, fig.width=8, fig.height=8}
load("plots_for_talk.rdata")
obs_v_pred
```

---









